---
title: "HSCT_GH_code"
author: "David Bennett"
date: "19/08/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(pander)
library(knitr)
library(BayesFactor)
library(ggplot2)
library(apaTables)
library(psych)
library(corrgram)
```


Arranged Data Frame

```{r}
HSCT_correct_RT2

HSCT_correct_RT2_2<-HSCT_correct_RT2 %>% 
  select(partID, Condition, ConditionSection, TimeTaken, Trial, MinusStatement, Column1) %>% 

filter(MinusStatement > 400) %>% 
 filter(partID > 44)%>%
  filter(partID!=47)%>%
  
  rename( error_rate = Column1) %>% 
  
 
  
  mutate(z_score = scale(MinusStatement, center=TRUE, scale = TRUE))
  
 HSCT_correct_RT2_2
  
```
  


Data frame for analysis of the non.inhibitory trials. Z scores were calculated but never used.

```{r}
non.inhib.<-HSCT_correct_RT2 %>% 
  select(ConditionSection, Condition, TimeTaken, partID, Trial, MinusStatement, error_rate) %>%
  filter(MinusStatement > 400) %>% 
 filter(partID > 44)%>%
  filter(partID!=47)%>%
  
  mutate(Condition = as.factor(Condition)) %>% 
  mutate(ConditionSection  = as.factor(ConditionSection)) %>%
  
  mutate(z_score = scale(MinusStatement, center=TRUE, scale = TRUE)) %>%  
 
  
  filter(Trial < 16)  

non.inhib.
```

Data frame for analysis of the inhibitory trials. Z scores were calculated but never used.

```{r}
inhib%>% 
  select(ConditionSection, Condition, TimeTaken, Trial, partID, MinusStatement, error_rate) %>%
  filter(MinusStatement > 400) %>% 
  filter(partID > 44)%>%
  filter(partID!=47)%>%
  
  mutate(Condition = as.factor(Condition)) %>% 
  mutate(ConditionSection  = as.factor(ConditionSection)) %>% 
  
  mutate(z_score = scale(MinusStatement, center=TRUE, scale = TRUE))%>%


filter(Trial > 15)  

inhib 
```

The overview (sd, median, and mean) of the 'time to sentence completion' data in both inhibitory and non-inhibitory conditions accross groups.

```{r}
non.inhib. %>% 
  
  filter(MinusStatement > 400) %>%
  group_by(Condition, ConditionSection) %>% 
  summarise(mean=mean(MinusStatement), median=median(MinusStatement), sd=sd(MinusStatement)) %>% 
  
   
 
  pander(caption="Mean, Median, and Standard deviation of reaction times in non-inhibitory condition.")

inhib %>% 
  filter(MinusStatement > 400) %>%
  group_by(Condition, ConditionSection) %>% 
  summarise(mean=mean(MinusStatement), median=median(MinusStatement), sd=sd(MinusStatement)) %>% 

 
  pander(caption= "Mean, Median, and Standard Deviation of reaction times in inhibitory condition.")
  
 
```

Overview of the error rate (sd and mean) data in both inhibitory and non-inhibitory trials accross groups.

```{r}
non.inhib. %>% 
 
  select(Condition,ConditionSection, Trial, error_rate, partID) %>% 
  group_by(Condition, ConditionSection) %>%
  filter(partID > 44)%>%
  filter(partID!=47)%>%

  summarise(mean=mean(error_rate), sd=sd(error_rate)) %>% 
  pander(caption= "Error rate (SD and Mean) in non-inhibitory condition")

  
  
inhib%>% 
  select(Condition,ConditionSection, Trial, error_rate, partID) %>% 
  group_by(Condition, ConditionSection) %>% 
filter(partID > 44)%>%
  filter(partID!=47)%>%
  summarise(mean=mean(error_rate),  sd=sd(error_rate)) %>% 
  
  pander(caption= "Error rate (SD and Mean) in inhibitory condition.")

```

ANOVA for interactions between group and trial type on the median of the 'time to sentence completion'.
No significance found f(2,38)=1.486, p=.23

```{r}
HSCTmedianRT %>% 
  group_by(Condition, ConditionSection, MinusStatement, Trial, partID) %>% 

  
  
 filter(MinusStatement > 400) %>% 
 filter(partID > 44)%>%
  filter(partID!=47) %>% 

summarise (median = median(MinusStatement, na.rm = TRUE))

HSCTmedianRT

lmABImed<-lm(median ~ ConditionSection + Condition, data = HSCTmedianRT)

lmreact<-lmABI

car::Anova(lmreact, type=3)


```

ANOVA for interactions between group and trial type on the error rate.
significance found f(2,38)=15.56, p=.000

```{r}
lm.error.data %>% 
  select(Condition, ConditionSection, MinusStatement, error_rate, Trial, partID) %>% 
  filter(MinusStatement > 400) %>% 
 filter(partID > 44)%>%
  filter(partID!=47)

lmerror<-lm(error_rate ~ ConditionSection + Condition, data = lm.error.data)

car::Anova(lmerror, type=3) 

```

Cohen d.
1. Error rate in non-inhib - non ABI.
No significant effect size d=0.11(negligable)

```{r}
error_rate.Cohen.d.nonABI %>% 
  select(Condition, ConditionSection, partID, MinusStatement, error_rate, Trial) %>% 
  filter(MinusStatement > 400) %>% 
 filter(partID > 44)%>%
  filter(partID!=47) %>% 
    filter(Condition=="Non-ABI") %>% 
  filter(Trial < 16)
  
  error_rate.Cohen.d.nonABI

  
cohen.d(error_rate~ConditionSection, data = error_rate.Cohen.d.nonABI)

```

2. Error rate in  inhib trials non-ABI group
No significant error size d=0.03(negligible)

```{r}
error_rate.inh.Cohen.d.nonABI<-HSCT_correct_RT2_2 %>% 
  select(Condition, ConditionSection, partID, MinusStatement, error_rate, Trial) %>% 
  filter(MinusStatement > 400) %>% 
 filter(partID > 44)%>%
  filter(partID!=47) %>% 
    filter(Condition=="Non-ABI") %>% 
  filter(Trial > 16)
  
  error_rate.inh.Cohen.d.nonABI

  
cohen.d(error_rate~ConditionSection, data = error_rate.inh.Cohen.d.nonABI)

```

3. Error rate in the non-inhib trials of ABIgroup
no significant effect size d=.13 (negligible)

```{r}
error_rate.Cohen.d.ABI<-HSCT_correct_RT2_2 %>% 
  select(Condition, ConditionSection, partID, MinusStatement, error_rate, Trial) %>% 
  filter(MinusStatement > 400) %>% 
 filter(partID > 44)%>%
  filter(partID!=47) %>% 
    filter(Condition=="ABI") %>% 
  filter(Trial < 16)
  
  error_rate.Cohen.d.ABI

  
cohen.d(error_rate~ConditionSection, data = error_rate.Cohen.d.ABI)
```

4. Error rate in the inhib trials of the ABI group
Significant effect size d=.43 (small)

```{r}
error_rate.Cohen.d.inh.ABI<-HSCT_correct_RT2_2 %>% 
  select(Condition, ConditionSection, partID, MinusStatement, error_rate, Trial) %>% 
  filter(MinusStatement > 400) %>% 
 filter(partID > 44)%>%
  filter(partID!=47) %>% 
    filter(Condition=="ABI") %>% 
  filter(Trial > 16)
  
  error_rate.Cohen.d.inh.ABI

  
cohen.d(error_rate~ConditionSection, data = error_rate.Cohen.d.inh.ABI)
```

Baysian analysis of models

1) response times
```{r}
anov.lmBF<-HSCT_correct_RT2_2 %>% 
  mutate_if(is.logical, factor)

  lmBF(MinusStatement~ConditionSection + Condition, data = HSCT_correct_RT2_2)
  

```

2) error rate

```{r}
error_rate.lmBF<-HSCT_correct_RT2_2 %>% 
  mutate_if(is.logical, factor)

  lmBF(error_rate~ConditionSection + Condition, data = HSCT_correct_RT2_2)



```

Plots

```{r}

plot1RT.inhib<-inhib %>% 
  
  ggplot(aes( ConditionSection, MinusStatement, group=Condition, color = Condition )) +
  stat_summary(geom="pointrange", fun.data=mean_se) +
  stat_summary(geom="line", fun.data=mean_se) +
  ylab("Time taken for statement completion (Ms)") +
  scale_color_discrete(name="") +
  xlab("")+
  coord_cartesian(ylim = c(1600, 3200))+
  
  theme(legend.background = element_rect(fill = "white"))+
  theme(legend.position = "bottom")+
  ggtitle("Inhibitory condition")
  

plot1RT.inhib

plot2RT.noninhib<-non.inhib. %>%  
  ggplot(aes( ConditionSection, MinusStatement, group=Condition, color=Condition)) +
  stat_summary(geom="pointrange", fun.data=mean_se) +
  stat_summary(geom="line",  fun.data=mean_se) +
  ylab("Time taken for statement completion (Ms)") +
  scale_color_discrete(name="") +
  xlab("")+
  coord_cartesian(ylim = c(1600, 3200))+
  theme(legend.background = element_rect(fill = "white"))+
  theme(legend.position = "bottom")+
  ggtitle("Non-inhibitory")

plot2RT.noninhib

plot1.inhib.error<-inhib %>% 
   ggplot(aes( ConditionSection, error_rate, group=Condition, color=Condition)) +
  stat_summary(geom="pointrange", fun.data=mean_se) +
  stat_summary(geom="line",  fun.data=mean_se) +
  ylab("Error rate") +
  scale_color_discrete(name="") +
  xlab("")+
  coord_cartesian(ylim = c(0, 0.5))+
  theme(legend.background = element_rect(fill = "white"))+
  theme(legend.position = "bottom")+
  ggtitle("Inhibitory condition")

plot1.inhib.error

plot2.noninhib.error<-non.inhib. %>% 
  ggplot(aes( ConditionSection, error_rate,group=Condition, color=Condition)) +
  stat_summary(geom="pointrange", fun.data=mean_se) +
  stat_summary(geom="line",  fun.data=mean_se) +
  ylab("Error rate") +
  scale_color_discrete(name="") +
  xlab("")+
  coord_cartesian(ylim = c(0, 0.5))+
  theme(legend.background = element_rect(fill = "white"))+
  theme(legend.position = "bottom")+
  ggtitle("Non-inhibitory condition")
  


plot2.noninhib.error

plotnon.inhibgroup<-non.inhib. %>% 
  filter(Condition=="ABI") %>% 
  ggplot(aes(ConditionSection, error_rate, group = partID ))+
  stat_summary(geom="pointrange") +
  stat_summary(geom="line")+
   ylab("Error rate") +
  xlab("")+
  
  
  ggtitle("Error rate for non-inhibitory condition:\nIndividual results (ABI)")+
  coord_cartesian(ylim = c(0, 1.6))
  


plotnon.inhibgroup 

plotnon.inhibgroupnonabi<-non.inhib. %>% 
  filter(Condition=="Non-ABI") %>% 
  ggplot(aes(ConditionSection, error_rate, group = partID ))+
  stat_summary(geom="pointrange") +
  stat_summary(geom="line")+
   ylab("Error rate") +
  xlab("")+
  
  
  ggtitle("Error rate for non-inhibitory condition:\nIndividual results (non-ABI)")+
  coord_cartesian(ylim = c(0, 1.6))
  


plotnon.inhibgroupnonabi 

plotinhibgroup<-inhib %>% 
  filter(Condition=="ABI") %>% 
  ggplot(aes(ConditionSection, error_rate, group = partID))+
  stat_summary(geom="pointrange") +
  stat_summary(geom="line")+
   ylab("Error rate") +
  coord_cartesian(ylim = c(0, 1.6))+
  
   
  xlab("")+
  
  ggtitle("Error rate for inhibitory condition: \nIndividual results (ABI)")

plotinhibgroup

plotinhibgroupnonabi<-inhib %>% 
  filter(Condition=="Non-ABI") %>% 
  ggplot(aes(ConditionSection, error_rate, group = partID))+
  stat_summary(geom="pointrange") +
  stat_summary(geom="line")+
   ylab("Error rate") +
  coord_cartesian(ylim = c(0, 1.6))+
  
   
  xlab("")+
  
  ggtitle("Error rate for inhibitory condition: \nIndividual results (non-ABI)")

plotinhibgroupnonabi
```

Arranging plots into grids.

```{r}

grid.arrange(plotnon.inhibgroup, plotnon.inhibgroupnonabi,plotinhibgroup, plotinhibgroupnonabi, ncol=2 )
g<-arrangeGrob(plotnon.inhibgroup,plotnon.inhibgroupnonabi,plotinhibgroup,plotinhibgroupnonabi, ncol=2)
ggsave(filename = "errorrateinhib.pdf", g)

grid.arrange(part73.non.inhib.plot, part58.noninhib.plot, part73.inhib.plot, part58.inhib.plot, ncol=2)
g<-arrangeGrob(part73.non.inhib.plot, part58.noninhib.plot, part73.inhib.plot, part58.inhib.plot, ncol=2)
ggsave(filename = "part73.58.pdf", g)

grid.arrange(plot1.inhib.error, plot2.noninhib.error, ncol=2 )
g<-arrangeGrob(plot1.inhib.error, plot2.noninhib.error, ncol=2)
ggsave(filename = "inhib.pdf", g)

grid.arrange(plot1RT.inhib, plot2RT.noninhib, ncol = 2)
g<-arrangeGrob(plot1RT.inhib, plot2RT.noninhib, ncol = 2)
ggsave(filename = "time to sentence completion.pdf", g)

```

